Retrofitting Effect Handlers onto OCaml

### 2020-11-17 retro-concurrency.tex
edits

\vspace{-2mm}
\subsection{Heap-allocated fibers}

@@

In this section, we measure the impact of the addition of effect handlers on
code that does not use effect handlers. Our macro benchmark suite consists of
54 real OCaml workloads including verification tools (|Coq|, |Cubicle|,
|AltErgo|), parsers (|menhir|, |yojson|), storage engines (|irmin|), utilities
(|cpdf|, |decompress|), bioinformatics (|fasta|, |knucleotide|, |revcomp2|,
|regexredux2|), numerical analysis (|grammatrix|, |LU_decomposition|) and
simulations (|nbody|, |game_of_life|). In addition to Stock (|stock|) and
Multicore OCaml (|MC|), we also ran the benchmarks on Multicore OCaml with no
red zone (|MC+RedZone0|) in the fiber (all OCaml functions will have stack
overflow check) and a red zone size of 32 words (|MC+RedZone32|). Recall that
the default red zone size in Multicore OCaml is 16 words.

>>>>

\vspace{-2mm}
\subsection{Heap-allocated fibers}
\label{sec:hafibers}

@@

In this section, we measure the impact of the addition of effect handlers on
code that does not use effect handlers. Our macro benchmark suite consists of
54 real OCaml workloads including verification tools (|Coq|, |Cubicle|,
|AltErgo|), parsers (|menhir|, |yojson|), storage engines (|irmin|), utilities
(|cpdf|, |decompress|), bioinformatics (|fasta|, |knucleotide|, |revcomp2|,
|regexredux2|), numerical analysis (|grammatrix|, |LU_decomposition|) and
simulations (|nbody|, |game_of_life|). In addition to Stock (|stock|) and
Multicore OCaml (|MC|), we also ran the benchmarks on Multicore OCaml with no
red zone (|MC+RedZone0|) in the fiber (all OCaml functions will have a stack
overflow check) and a red zone size of 32 words (|MC+RedZone32|). Recall that
the default red zone size in Multicore OCaml is 16 words (\S\ref{sec:hafibers}).
